% sage_latex_guidelines.tex V1.20, 14 January 2017

\documentclass[Afour,sageh,times]{sagej}

\usepackage{moreverb,url}

\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\def\volumeyear{2016}

\begin{document}

\runninghead{Fabbri and Estrada}

\title{Communicability-derived layout and community detection in complex networks}

\author{Renato Fabbri\affilnum{1} and Ernesto Estrada\affilnum{2}}

\affiliation{\affilnum{1}Institute of Mathematics and Computer Sciences,
University of S達o Paulo,
S達o Carlos, Brazil\\
\affilnum{2} Department of Mathematics and Statistics, University of Strathclyde, Glasgow G11HX, United Kingdom}

\corrauth{Renato Fabbri,
Institute of Mathematics and Computer Sciences,
University of S達o Paulo,
S達o Carlos
13566-590, Brazil.}

\email{renato.fabbri@gmail.com}

\begin{abstract}
This paper describes the use of the communicability measure for the achievement
  of layouts and community detection in complex networks.
\end{abstract}

\keywords{Complex networks, communicability, community detection, layout algorithms, interactive visualization}

\maketitle

\section{Introduction}
\subsection{Related work}
\section{The communicability framework}
\subsection{Preliminaries}
\subsection{Layouts}
\subsection{Community detection}
\section{Results}
\subsection{An interactive interface}
\subsection{Use cases}

\section{Conclusions and further work}
\begin{acks}
This class file was developed by Sunrise Setting Ltd,
Brixham, Devon, UK.\\
Website: \url{http://www.sunrise-setting.co.uk}
\end{acks}

\begin{thebibliography}{99}
\bibitem[Kopka and Daly(2003)]{R1}
Kopka~H and Daly~PW (2003) \textit{A Guide to \LaTeX}, 4th~edn.
Addison-Wesley.

\bibitem[Lamport(1994)]{R2}
Lamport~L (1994) \textit{\LaTeX: a Document Preparation System},
2nd~edn. Addison-Wesley.

\bibitem[Mittelbach and Goossens(2004)]{R3}
Mittelbach~F and Goossens~M (2004) \textit{The \LaTeX\ Companion},
2nd~edn. Addison-Wesley.

\end{thebibliography}

\end{document}
